\documentclass[11pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\signature{Yongjun Kim\\Department of Software\\Ajou University\\Suwon 16499, Republic of Korea\\yjkim0123@ajou.ac.kr}

\address{Yongjun Kim\\Department of Software\\Ajou University\\Suwon 16499, Republic of Korea}

\begin{document}

\begin{letter}{Editor-in-Chief\\Journal of Power Sources\\Elsevier}

\opening{Dear Editor,}

We are pleased to submit our manuscript entitled ``\textbf{When Does Transfer Learning Help for Battery Life Prediction? A Cautionary Empirical Study on Cross-Condition Knowledge Transfer}'' for consideration as a regular article in the \textit{Journal of Power Sources}.

Transfer learning (TL) has gained considerable attention in the battery community as a way to leverage degradation data across operating conditions. However, most studies report only positive results, leaving practitioners without guidance on when TL might fail. Our study addresses this gap through the first systematic evaluation of seven TL methods across 14 transfer scenarios using 213 Samsung INR21700-50E cells aged under 71 distinct conditions.

Our key findings are:
\begin{itemize}
    \item Within the same cell chemistry, TL provides statistically significant benefit in only one out of six cross-temperature transfer directions (to 23\textdegree C, $p = 0.019$).
    \item Transfer to high-temperature conditions (45\textdegree C) produces statistically significant \textit{negative} transfer ($p < 0.03$), traced to a feature importance shift across temperature domains.
    \item Calendar-to-cyclic transfer always fails, confirming that different degradation mechanisms cannot be bridged by standard TL.
\end{itemize}

We believe these cautionary findings are timely and relevant for the battery modeling community, providing practical guidelines for when TL should and should not be applied. The manuscript uses a fair comparison protocol with identical base learners for all methods, addressing a common methodological concern in TL benchmarks.

All data used in this study are publicly available (Figshare DOI: 10.6084/m9.figshare.25975315.v1), and analysis code is available at \url{https://github.com/yjkim0123/battery-transfer-learning}.

This manuscript has not been published or submitted elsewhere. We have no conflicts of interest to declare.

Thank you for your consideration.

\closing{Sincerely,}

\end{letter}
\end{document}
